State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some small paper edits and committing to merge with parham

This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for higher order systems via a systematic model reduction procedure. In addition, a method is presented for estimating the connectivity structure and the synaptic time constant. Until now, estimation of local intracortical connectivity structure has not been attempted. Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}. The key development in that work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of observations (recording electrodes in this case). In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of the technique to neural fields.

@@

\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC or Amari style neural field model \cite{Wilson1973,Amari1977} that was used to create our intracortical connectivity estimator. Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials. They are popular due to being parsimonious yet having a strong link with the underlying physiology. Each neural population represents a functional cortical processing unit, such as a column. The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns. In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}. Locally, each column is thought be connected via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}. For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}. Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}. 
Field models are also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.

@@

The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function 
\begin{equation}
	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \varsigma \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}. 
\end{equation}
The parameters $f_{max}$ and $v_0$ describe the maximum firing rate and firing threshold of the neural populations. The parameter $\varsigma$ governs the slope of the sigmoid. By substituting equation~\ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model 
\begin{eqnarray}
	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) &=&  \int_{-\infty}^t h\left(t - t'\right) \\
	&\times&\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}'dt'. \nonumber
\end{eqnarray}
To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function 
\begin{equation}
	\label{GreensFuncDef} Dh\left( t \right) = \delta \left( t \right), 
\end{equation}
where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
\begin{eqnarray}
	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} &+& \zeta v\left( \mathbf{r},t \right) = \\
	&&\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. \nonumber
\end{eqnarray}
To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see Appendix~\ref{Time Discretization}) giving 
\begin{eqnarray}
	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\ 
	&+& e_t\left(\mathbf{r}\right), 
\end{eqnarray}
where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is i.i.d. such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$. This term was added to account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
\begin{equation}
	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)d\mathbf{r}'} + \boldsymbol{\varepsilon}_t, 
\end{equation}
where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$. The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the geometry of pick-up range of sensors where 
\begin{equation}
	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)}. 
\end{equation}

@@

where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$. The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model~\cite{Coombes2005}. The width and positioning of the basis function can be determined by spectral analysis explain in detail in Section~\ref{SpectralAnalysisSection}. The connectivity kernel can also be considered a decomposition into a set of basis functions in 

@@

% \begin{equation}
% \mathbf{C} = \left[\begin{array}{{cccc}}
% \int_{\Omega}m(\mathbf{r}_1 - \mathbf{r}')\boldsymbol{\phi}_1(\mathbf{r}')d\mathbf{r}' & \int_{\Omega} m(\mathbf{r}_1 - \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r' & \dots
% &\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
% r')d\mathbf r' \\
% \int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol \phi_1(\mathbf
% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_2 -
% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
% \vdots&\vdots&\ddots&\vdots\\
% \int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol \phi_1(\mathbf
% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_{n_y} -
% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
% \end{array}\right],
% \end{equation}
% and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the membrane voltage from sampled observations \cite{Sanner1992,Scerri2009}. Based on a two dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.

@@

Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$. Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited. Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}} \omg{will try to find something. These kernel are kinda theoretical and I have not ever seen and estimate of the covariance function. Can we remove the sentence ``Such a condition is usually satisfied...'' }. Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 2-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$. Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy 
\begin{equation}
	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho_s\nu_{c}}, 
\end{equation}
where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter. This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$. If the condition is not satisfied, spatial aliasing will occur.

There are two options available to alleviate problems with aliasing. The first, which is the most desirable, is to increase the spatial sampling frequency (using a higher resolution of sensors). The second is to use wider sensors, where the spatial averaging acts like a low-pass anti-aliasing filter. This option is a compromise between alleviating issues with aliasing and loosing high frequency information contained in the field. In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations. However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}. Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics. However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}. This is further illustrated our results.

Similar considerations need to be made regarding the representation of the dynamic field $v_t(\mathbf{r})$ using the basis function decomposition. The minimum distance between adjacent basis functions must also satisfy Shannon's sampling theorem to capture the dominant spectral information of the field. Thus, the minimum distance between basis functions must satisfy 
\begin{equation}\label{eq:BasisFunctionSeparation}
	\Delta_b < \frac{1}{2\rho_b\nu_{co}}. 
\end{equation}
where $\rho_b$ is an over-sampling parameter to determine the basis function separation and $\nu_{co}$ is the spatial cut-off frequency from the observation. For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis width parameter $\sigma_{\phi}^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}. The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
\begin{equation}\label{eq:GaussianFT}
\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
\end{equation}
where 
\begin{equation}\label{eq:GaussianFTWidth}
	\sigma^2_{\nu} = \frac{1}{\pi^2\sigma_{\phi}^2}. 
\end{equation}
The basis function width, $\sigma^2_{\nu}$, should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_{co}$ giving
\begin{equation}\label{eq:WidthFrequencyRelationship}
 \sigma^2_{\nu}=\frac{2\boldsymbol\nu_c^\top \boldsymbol\nu_c}{\ln 2}.
\end{equation}
This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co} $. Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in Appendix~\ref{ap:FrequencyAnalysis}.
% Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.

>>>>

This paper extends the work of Schiff and Sauer~\cite{schiff2008kalman} by establishing a framework for estimating the state of the WC equations for higher order systems via a systematic model reduction procedure. In addition, a method is presented for estimating the connectivity structure and the synaptic time constant. Until now, estimation of local intracortical connectivity structure has not been reported (to the best of the authors knowledge). Recently, it has been shown that it is possible to estimate local coupling of spatiotemporal systems using techniques from control systems theory and machine learning \cite{Dewar2009}. The key development in that work was to represent the spatiotemporal system as a standard state-space model with an order independent of the number of observations (recording electrodes in this case). In addition, the appropriate model selection tools have been developed \cite{Scerri2009} allowing for the application of the technique to neural fields.

@@

\section{Neural Field Model}\label{NeuralModelSection} In this section, we describe a variant of the WC or Amari style neural field model \cite{Wilson1973,Amari1977} that was used to create our intracortical connectivity estimator. Neural field models relate mean firing rates of pre-synaptic neural populations to mean post-synaptic membrane potentials. They are popular due to being parsimonious yet having a strong link with the underlying physiology. Each neural population represents a functional cortical processing unit, such as a column. The columnar organisation of the cortex is continuous, where pyramidal cells are members of many columns. In general, cortical structure can be modelled in a physiologically plausible manner as being locally homogeneous (in short range intracortical connectivity) and heterogeneous (in long range cortico-cortical and corticothalamic connectivity)~\cite{Jirsa2009,Qubbaj2007}. In certain regoins of the cortex, each column is thought be connected locally via symmetric short range local excitation, with surround inhibition \cite{Braitenberg1998}. For example, this structural organisation is most studied in the visual system, where the surrounding inhibition effectively tunes a cortical column to a particular receptive visual field~\cite{Sullivan2006}. Neural field models are descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations, and epileptic behaviour~\cite{David2003,Bressloff2001,Breakspear2006}. 
Field models are also capable of generating complex patterns of activity such as Turing patterns, spirals, and traveling oscillations~\cite{Amari1977,Coombes2005,Coombes2007}.

@@

The firing rate of the presynaptic neurons is related to the postsynaptic membrane potential by the sigmoidal activation function 
\begin{equation}
	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{f_{max}\left(\mathbf{r}\right)}{1 + \exp \left( \varsigma \left( v_0\left( \mathbf{r} \right) - v\left(\mathbf{r}',t\right) \right) \right)}. 
\end{equation}
The parameters $f_{max}$ and $v_0$ describe the maximum firing rate and firing threshold of the neural populations. The parameter $\varsigma$ governs the slope of the sigmoid. By substituting equation~\ref{RateBasedInteractions} into \ref{SpikesToPotential} we get the spatiotemporal model 
\begin{eqnarray}
	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) &=&  \int_{-\infty}^t h\left(t - t'\right) \\
	&\times&\int_\Omega w\left(\mathbf{r},\mathbf{r}'\right) f\left( v\left( \mathbf{r}',t \right)\right)d\mathbf{r}'dt'. \nonumber
\end{eqnarray}
To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function 
\begin{equation}
	\label{GreensFuncDef} Dh\left( t \right) = \delta \left( t \right), 
\end{equation}
where $D=\frac{d}{dt} + \zeta$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function giving 
\begin{eqnarray}
	\label{FinalFormContinuous} \frac{dv\left( \mathbf{r},t \right)}{dt} &+& \zeta v\left( \mathbf{r},t \right) = \\
	&&\int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. \nonumber
\end{eqnarray}
To arrive at the integro-difference equation (IDE) form of the model we discretise time using a first-order Euler method (see~\ref{Time Discretization}) giving 
\begin{eqnarray}
	\label{DiscreteTimeModel} v_{t+1}\left(\mathbf{r}\right) &=& \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'} \nonumber\\ 
	&+& e_t\left(\mathbf{r}\right), 
\end{eqnarray}
where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is i.i.d. such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$. This term was added to account for uncertainty in the model. To generate iEEG/LFP data we used the output function 
\begin{equation}
	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)d\mathbf{r}'} + \boldsymbol{\varepsilon}_t, 
\end{equation}
where $\mathbf{r}_n$ defines the location of the sensors in the field where $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\Sigma_{\varepsilon}\right)$. The output kernel $m(\mathbf{r}-\mathbf{r}')$ governs the geometry of pick-up range of sensors where 
\begin{equation}
	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)}. 
\end{equation}

@@

where $\mathbf{\boldsymbol{\phi}}(\mathbf{r})$ is a vector of Gaussian basis functions that are scaled by the state vector, $\mathbf{x}_t$. The choice of Gaussian basis functions can be justified by the existence of the so called bump solutions for this class of model, which have a Gaussian shape~\cite{Coombes2005}. The width and positioning of the basis function can be determined by spectral analysis (explained in detail in Section~\ref{SpectralAnalysisSection}). The connectivity kernel can also be considered a decomposition into a set of basis functions in 

@@

% \begin{equation}
% \mathbf{C} = \left[\begin{array}{{cccc}}
% \int_{\Omega}m(\mathbf{r}_1 - \mathbf{r}')\boldsymbol{\phi}_1(\mathbf{r}')d\mathbf{r}' & \int_{\Omega} m(\mathbf{r}_1 - \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r' & \dots
% &\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
% r')d\mathbf r' \\
% \int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol \phi_1(\mathbf
% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_2 -
% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
% \vdots&\vdots&\ddots&\vdots\\
% \int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol \phi_1(\mathbf
% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_{n_y} -
% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
% \end{array}\right],
% \end{equation}
% and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations \cite{Sanner1992,Scerri2009}. Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.

@@

Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$. Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited. Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}} \omg{will try to find something. These kernel are kinda theoretical and I have not ever seen and estimate of the covariance function. Can we remove the sentence ``Such a condition is usually satisfied...'' }. Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the two-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$. Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy 
\begin{equation}
	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho_s\nu_{c}}, 
\end{equation}
where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter. This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$. If the condition is not satisfied, spatial aliasing will occur.

There are two options available to alleviate problems with aliasing. The first, which is the most desirable, is to increase the spatial sampling frequency (using a higher resolution of sensors). The second is to use wider sensors, where the spatial averaging acts like a low-pass anti-aliasing filter. This option is a compromise between alleviating issues with aliasing and loosing high frequency information contained in the field. In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations. However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}. Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics. However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}. This is further illustrated our results.

Similar considerations need to be made regarding the representation of the dynamic field $v_t(\mathbf{r})$ using the basis function decomposition. The minimum distance between adjacent basis functions must also satisfy Shannon's sampling theorem to capture the dominant spectral information of the field. Thus, the minimum distance between basis functions must satisfy 
\begin{equation}\label{eq:BasisFunctionSeparation}
	\Delta_b < \frac{1}{2\rho_b\nu_{co}}. 
\end{equation}
where $\rho_b$ is an over-sampling parameter to determine the basis function separation and $\nu_{co}$ is the spatial cut-off frequency from the observation. For the Gaussian basis functions, $\phi(\mathbf{r})$, being considered, the basis function width parameter, $\sigma_{\phi}^2$, can also be inferred using spectral considerations~\cite{Sanner1992,Scerri2009}. The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
\begin{equation}\label{eq:GaussianFT}
\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right),
\end{equation}
where 
\begin{equation}\label{eq:GaussianFTWidth}
	\sigma^2_{\nu} = \frac{1}{\pi^2\sigma_{\phi}^2}. 
\end{equation}
The basis function width, $\sigma^2_{\nu}$, should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_{co}$ giving
\begin{equation}\label{eq:WidthFrequencyRelationship}
 \sigma^2_{\nu}=\frac{2\boldsymbol\nu_c^\top \boldsymbol\nu_c}{\ln 2}.
\end{equation}
This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_{co} $. Proofs for equations~\ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} are given in~\ref{ap:FrequencyAnalysis}.
% Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
